### 2018-08-07 paper/security-discussion.tex
Fixes typos in security discussion

Stateless routing can result in re-ordered chunks or packets, and
chunks received on different devices of a user's squad. From Sphinx,
we inherit IDs for packets that we we include in the out-of-band
metadata on the file to be exchanged, as an ordered list, that is used
to re-order chunks if need be. The squad overlay handles inter-squad
device coordination. Liveness despite the possibility of squad devices
going offline during transfer or other node or link failures is
ensured by acknowledgments and timeouts as detailed in
~\cref{sec:squad_overlay}.

>>>>

Stateless routing can result in re-ordered chunks or packets, and
chunks received on different devices of a user's squad. From Sphinx,
we inherit IDs for packets that we we include in the out-of-band
metadata on the file to be exchanged, as an ordered list, that is used
to re-order chunks if need be. The squad overlay handles inter-squad
device coordination. Liveness despite the possibility of squad devices
going offline during transfer or other node or link failures is
ensured by acknowledgements and timeouts as detailed in
\cref{sec:squad_overlay}.
